---
name: Daniel Kirkland
title: "Music Insights"
output: html_notebook
---

First we need to use Tidyverse to handle data importing and wranging...

```{r}
  library(tidyverse)

survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")

```
```{r}
nrow(survey)
colnames(survey)

View(survey)
View(preferences)

```
Cleaning dataframes column names

```{r}
colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonymn"
colnames(survey)

```

Resetting column names to shorter, succinct 

```{r}
  colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonymn"
  colnames(survey)[colnames(survey) == "Timestamp"] <- "time_submitted"
  colnames(survey)[colnames(survey) == "Sex"] <- "sex"
  colnames(survey)[colnames(survey) == "What is your pseudonym?"] <- "pseudonym"
  colnames(survey)[colnames(survey) == "Major"] <- "academic_major"
  colnames(survey)[colnames(survey) == "Academic Year"] <- "academic_level"
  colnames(survey)[colnames(survey) == "Year you were born (YYYY)"] <- "year_born"
  colnames(survey)[colnames(survey) == "Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument_list"
  colnames(survey)[colnames(survey) == "Artist"] <- "favorite_song_artist"
  colnames(survey)[colnames(survey) == "Song"] <- "favorite_song"
  colnames(survey)[colnames(survey) == "Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"
  colnames(survey)
  View(survey)
  
  colnames(preferences)[colnames(preferences) == "Timestamp"] <- "time_submitted"
  colnames(preferences)[colnames(preferences) == "What was your pseudonym?"] <- "pseudonym"
  
  View(preferences)
```

Installing the dplyr library

```{r}
  library(dplyr)
```

Creating a tibble for our table "Person", using column data from survey.
Creating a tibble for our table "Favorite_song" using column data from preferences.


```{r}
  Person <- tibble(pseudonym = survey$pseudonym, sex = survey$sex, academic_major = survey$academic_major, academic_level = survey$academic_level, time_submitted = survey$time_submitted)

  View(Person)
  
  Favorite_song <- tibble(pseudonym = preferences$pseudonym, time_submitted = preferences$time_submitted)
  
  View(Favorite_song)
  
```

Changing date time format.  

```{r}
  library(readr)
  ?parse_datetime
  Person$time_submitted <- as.POSIXlt(parse_datetime(Person$time_submitted, format="%m/%d/%y %H:%M"))
  
  View(Person)

```

Observing factors for academic_level

```{r}
  levels(Person$academic_level)

```
Convert the column to a factor column. 

```{r}
  Person$academic_level <- as.factor(Person$academic_level)
  levels(Person$academic_level)
```

Observe factors for academic_major


```{r}
  Person$academic_major <- as.factor(Person$academic_major)
  levels(Person$academic_major)

```
Change some values (factors) for Person$academic_major, ex. remove one of the CIS entries: Computer information systems (or) Computer Information Systems. 

We're making a comparison change.  If you see this/these, change it to this to new value/s. Also, change it in the list of levels.    

```{r}
  levels(Person$academic_major)[levels(Person$academic_major) == "Computer     information systems"] <- "Computer Information Systems"
  levels(Person$academic_major)
```

Create a "ratings" table. Variables will be: pseudonym, artist_song, rating.  

First, create a copy of 'preference' and tranform the table. 

```{r}
  preferences_copy <- preferences
  View(preferences_copy)

```
Now transform the 'preferences_copy' table's artist_song columns into one column.

```{r}
  gather(preferences_copy, key = "artist_song", value = "rating", 3:45)
  View(preferences_copy)
```

Create a tibble from the 'preferences_copy' dataframe. 

```{r}
   Ratings <- tibble(pseudonym = preferences_copy$pseudonym, artist_song = preferences_copy$artist_song, rating = preferences_copy$rating)
  
  View(Ratings) 

```








