---
name: Daniel Kirkland
title: "Music Insights"
output: html_notebook
---

First we need to use Tidyverse to handle data importing and wranging...

```{r}
  library(tidyverse)

survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")

```
```{r}
nrow(survey)
colnames(survey)

View(survey)
View(preferences)

```
Cleaning dataframes column names

```{r}
colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonymn"
colnames(survey)

```

Resetting column names to shorter, succinct 

```{r}
  colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonymn"
  colnames(survey)[colnames(survey) == "Timestamp"] <- "time_submitted"
  colnames(survey)[colnames(survey) == "Sex"] <- "sex"
  colnames(survey)[colnames(survey) == "What is your pseudonym?"] <- "pseudonym"
  colnames(survey)[colnames(survey) == "Major"] <- "academic_major"
  colnames(survey)[colnames(survey) == "Academic Year"] <- "academic_level"
  colnames(survey)[colnames(survey) == "Year you were born (YYYY)"] <- "year_born"
  colnames(survey)[colnames(survey) == "Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument_list"
  colnames(survey)[colnames(survey) == "Artist"] <- "favorite_song_artist"
  colnames(survey)[colnames(survey) == "Song"] <- "favorite_song"
  colnames(survey)[colnames(survey) == "Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"
  colnames(survey)
  View(survey)
  
  colnames(preferences)[colnames(preferences) == "Timestamp"] <- "time_submitted"
  colnames(preferences)[colnames(preferences) == "What was your pseudonym?"] <- "pseudonym"
  
  View(preferences)
```

Installing the dplyr library

```{r}
  library(dplyr)
```

Creating a tibble for our table "Person", using column data from survey.
Creating a tibble for our table "Favorite_song" using column data from preferences.


```{r}
  Person <- tibble(pseudonym = survey$pseudonym, sex = survey$sex, academic_major = survey$academic_major, academic_level = survey$academic_level, time_submitted = survey$time_submitted)

  View(Person)
  
  Favorite_song <- tibble(pseudonym = preferences$pseudonym, time_submitted = preferences$time_submitted)
  
  View(Favorite_song)
  
```
Creating a tibble for our table "Favorite Song", using column data for each column we want to include in our table.  

```{r}
  View(preferences)  
  Favorite_Song<-
```

```{r}
  library(readr)
  ?parse_datetime
  Person$time_submitted <- as.POSIXlt(parse_datetime(Person$time_submitted, format="%m/%d/&Y %H:%M"))
  
  View(Person)

```

















